---
title: "writeup_pt2"
output: html_document
---
# # RMarkdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Library Import

```{r}
library(tidyverse)
library(babynames)

```
# # Splash
#Madison Charts
```{r}

babynames %>%
  filter(name == "Madison", sex=="F") %>%
  #filter(year>=1960) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) +
  labs(title = "Girls Named Madison: The Influence of Splash", subtitle = "Splash was released in 1984", y = "babies") +
    geom_vline(aes(xintercept = 1984),
             linetype = "dashed",
             color = "red",
             size = 1)
  ggsave("madisongirls.png")


babynames %>%
  #filter(name %in% c("Daryl")) %>%
  filter(name == "Madison", sex=="M") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) +
    geom_vline(aes(xintercept = 1983),
             linetype = "dashed",
             color = "red",
             size = 1) + 
  labs(title = "Boys Named Madison", subtitle = "Splash was released in 1983", y = "babies")
ggsave("madisonboys.png")




  
```


#Madison Calculations

```{r}
mad_pre_splash <- babynames %>% 
  filter(name == "Madison", sex == "F", year < 1984) %>% 
  summarise(use = sum(n), avg = mean(n))

mad_pre_splash

mad_splash_to_90 <- babynames %>% 
  filter(name == "Madison", sex == "F", year >= 1984, year <1990) %>%
  group_by(year) %>% 
  summarise(use = sum(n))

mad_splash_to_90

mad_to_90_total <- 
  mad_splash_to_90 %>% 
  summarise(total = sum(use))

mad_to_90_total

mad_splash_to_present <- babynames %>% 
  filter(name == "Madison", sex == "F", year >= 1984)
  #group_by(year) 
  #summarise(use = sum(n))

mad_splash_to_present

avg_boys_mad_up_to_splash <- babynames %>% 
  filter(name == "Madison", sex=="M", year <1984) %>%
  summarise(avg = mean(n))

avg_boys_mad_postsplash <- babynames %>% 
  filter(name == "Madison", sex=="M", year >=1984) %>%
  summarise(avg = mean(n))
```

# # Bewitched

```{r}
bewitched <- c("Samantha", "Darren", "Endora", "Tabitha")

bw_adult <- data.frame(
  
  name = c("Samantha", "Darren", "Endora"),
  year = c(1964, 1964, 1964)
  
)

bw_baby <- data.frame(
  name = "Tabitha",
  year = 1966
  
)


babynames %>%
  filter(name %in% bewitched) %>%
  filter(year>=1940) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = year),
             linetype = "dashed",
             color = "red",
             data = bw_adult,
             size = 1
             ) + 
  geom_vline(aes(xintercept = year),
             linetype = "dashed",
             color = "navy",
             data = bw_baby,
             size = 1
             ) + 
  labs(title = "Bewitched Characters", subtitle = "Bewitched began airing in 1964, the character Tabitha was born in 1966", y = "babies")

ggsave("bewitched.png")
```

# # Twilight

```{r}


babynames %>%
  filter(name %in% c("Edward", "Esme", "Carlisle", "Emmett", "Alice", "Rosalie", "Jasper", "Bella")) %>%
  filter(year>=2000) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
   
  geom_vline(aes(xintercept = 2005),
             linetype = "dashed",
             color = "red", ) +
    geom_vline(aes(xintercept = 2008),
             linetype = "dashed",
             color = "navy",
             ) +
  facet_wrap(~name, scales = "free_y") + 
  labs(title = "Twilight Series Characters", subtitle = "The first Twilight book was released in 2005; the first movie came out in 2008", y = "babies")

ggsave("twilight.png")

```


# # Harry Potter


# Names First Apear

```{r}

newhp <- c("Draco", "Hermione", "Sirius", "Bellatrix", "Severus")

bookyears <- c(1997, 1997, 1999, 2003, 2007)

movieyears <- c(2001, 2001, 2004, 2007, 2011)

hp_new_book <- data.frame(
  
  name = newhp,
  
  year = bookyears,
  
  release = c("Book 1", "Book 1", "Book 3", "Book 5", "Book 7")
)

hp_new_movie <- data.frame(
  
  name = newhp,
  
  year = movieyears,
  
  release = c("Movie 1", "Movie 1", "Movie 3", "Movie 5", "Movie 8")
)



babynames %>%
  filter(name %in% newhp) %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x = year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = year, color = release),
             linetype="dashed",
             data = hp_new_book, 
             size = 1) + 
  
  geom_vline(aes(xintercept = year, color = release),
             linetype="dashed",
             data = hp_new_movie, 
             size = 1) +
  
  labs(title = "Names Introduced by Harry Potter Series", subtitle = "First appearence or major character revelation (Snape)")
ggsave("hpnew.png")

```

# Luna

```{r}

hp5_yrs <- data.frame(
  
  release = c("Book Release", "Movie Release"),
  
  yr = c(2003, 2007)
  
)

book5names <- c("Luna")

babynames %>%
  filter(name %in% book5names) %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x = year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = yr, color = release),
             linetype="dashed",
             data = hp5_yrs, 
             size = 1) + 
  labs(title = "Luna Lovegood: Making 'Nerdy' Cool Since 2003", subtitle = "Luna Lovegood is first featured in the fifth book (2003) / movie (2007)", y = "babies")
ggsave("lunalovegood.png")


```


# # 50 Shades

```{r}
babynames %>%
  filter(name %in% c("Christian", "Anastasia")) %>%
  filter(year>=2000) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 2011),
             linetype = "dashed",
             color = "red",
             size = 1) + 
    geom_vline(aes(xintercept = 2015),
             linetype = "dashed",
             color = "navy",
             size = 1) + 
  labs(title = "50 Shades of Gray Characters", subtitle = "The first book came out in 2011; the first movie was released in 2015", y = "babies")

ggsave("50shades.png")
```


# # Friends

```{r}

names <- c("Chandler", "Monica", "Ross", "Rachel", "Phoebe", "Joey", "Monica")
important_dates <- data.frame(
  name=names,
  year=c(1994, 1994, 1994, 1994, 1994, 1994, 1998),
  update= c("Friends First Airs","Friends First Airs", "Friends First Airs", "Friends First Airs","Friends First Airs", "Friends First Airs", "Scandal Breaks" )
)
babynames %>%
  filter(name %in% names) %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, fill = sex), color = "black", stroke = 0.2, size = 1.5, shape = 21) + 
  facet_wrap(~name, scales = "free_y") +
  geom_vline(aes(xintercept = year, color = update),
             linetype="dashed",
             data = important_dates,
             size = 1) + 
  labs (title = "Friends Characters", subtitle = "Friends began airing in 1994; the Lewinsky-Clinton Scandal broke in 1998", y = "babies")

ggsave("friends.png")

```

# # Kardashians

# First Gen

```{r}
babynames %>%
  filter(name %in% c("Kim", "Khloe", "Kris", "Kylie", "Kendall", "Kourtney")) %>%
  filter(year>=1980, sex == "F") %>% 
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = name)) + 
  facet_wrap(~name, scales = "free_y") +  geom_vline(aes(xintercept = 2007),
             linetype = "dashed",
             color = "red",
             size = 1) + 
  labs(title = "Kardashian Family", subtitle = "Keeping Up with the Kardashians began airing in 2007", y = "babies")

ggsave("dash1stgen.png")

```

# Kourtney Khloe

```{r}

babynames %>%
  filter(name %in% c("Chloe", "Khloe")) %>%
  filter(year>=1990, sex == "F") %>% 
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") +  geom_vline(aes(xintercept = 2007),
             linetype = "dashed",
             color = "red",
             size = 1) + 
  labs(title = "Chloe/Khloe: The Influence of the Kardashian Family", subtitle = "Keeping Up with the Kardashians began airing in 2007", y = "babies")
  

ggsave("CKhloe.png")


babynames %>%
  filter(name %in% c("Courtney", "Kourtney")) %>%
  filter(year>=1990, sex=="F") %>% 
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") +  geom_vline(aes(xintercept = 2007),
             linetype = "dashed",
             color = "red",
             size = 1) + 
  labs(title = "Courtney/Kourtney: The Influence of the Kardashian Family", subtitle = "Keeping Up with the Kardashians began airing in 2007", y = "babies")

ggsave("CKourtney.png")

```

# Next Gen


```{r}
kidsnames <- c("Mason", "Penelope", "Reign", "North", "Saint", "Dream")

kardashian_kids <- data.frame( 
  name = kidsnames, year = c(2009, 2012, 2014, 2013, 2015, 2016)
  
  )

babynames %>%
  filter(name %in% kidsnames) %>%
  filter(year>=2000) %>% 
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") +  
  
    geom_vline(aes(xintercept = year),
             linetype = "dashed",
             color = "red",
             data = kardashian_kids,
             size = 1) + 
  labs(title = "Names of Kardashian Children Born Before 2017", subtitle = "Vertical line denotes birth years", y = "babies")

ggsave("dash2ndgen.png")
```

# # Charlie's Angels

# All
```{r}
winslet <- data.frame (
  
  name = c("Kate","Kate", "Sabrina"),
  year = c(1997, 1995, 1996)
) #To be hihglighted later


babynames %>%
  filter(name %in% c("Farrah", "Kate", "Jaclyn", "Sabrina", "Jill", "Kelly")) %>%
  filter(year>=1950, sex == "F") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red",
             size =1) + 
  labs(title = "Charlie's Angels Characters and Actresses", subtitle = "Charlie's Angels premiered in 1976", y = "babies")
ggsave("charliesangels.png")
```

#Charlie

```{r}

babynames %>%
  filter(name == "Charlie", sex == "M") %>%
  filter(year>=1960) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red") + 
    labs(title = "Boys Named Charlie: Charlie's Angels", subtitle = "Charlie's Angels premiered in 1976", y = "babies")

```

# Characters

```{r}

babynames %>%
  filter(name %in% c( "Sabrina", "Jill", "Kelly")) %>%
  filter(year>=1960) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red",
             size = 1)


babynames %>%
  filter(name %in% c( "Jill"), sex == "F") %>%
  filter(year>=1950) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red",
             size = 1) + 
      labs(title = "Girls Named Jill: Charlie's Angels", subtitle = "Charlie's Angels premiered in 1976", y = "babies")
ggsave("jillmunroe.png")


babynames %>%
  filter(name %in% c( "Jillian"), sex == "F") %>%
  filter(year>=1950) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red",
             size = 1) + 
      labs(title = "Full Name: Jillian", subtitle = "Influence of Jill Monroe", y = "babies")
ggsave("jillian.png")


spellman <- data.frame (
  
  year = c(1976, 1996),
  release = c("1976 \n Sabrina Duncan \n", "1996 \n Sabrina Spellman \n" )
  
)

babynames %>%
  filter(name %in% c( "Sabrina")) %>%
  filter(year>=1950, sex == "F") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = release),
             linetype = "dashed",
             data = spellman,
             size = 1) + 
   labs(title = "Girls Named Sabrina: Charlie's Angels and Other Influences", subtitle = "Charlie's Angels premiered in 1976; Sabrina the Teenage Witch premiered in 1996", y = "babies")
ggsave("sabrinaduncan.png")
  



babynames %>%
  filter(name %in% c( "Kelly"), sex=="F") %>%
  filter(year>=1950) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red",
             size = 1) + 
  labs(title = "Girls Named Kelly: Charlie's Angels", subtitle = "Charlie's Angels premiered in 1976", y = "babies")

ggsave("kellygarrett.png")
```





# Actresses 

```{r}
babynames %>%
  filter(name %in% c( "Farrah")) %>%
  filter(year>=1950, sex == "F") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 1976),
             linetype = "dashed",
             color = "red",
             size = 1) + 
   labs(title = "Girls Named Farrah: Charlie's Angels", subtitle = "Farrah Fawcett starred in Charlie's Angels from 1976 - 1977", y = "babies")
ggsave("farrahfawcett.png")

winslet <- data.frame (
  
  #name = c("Kate","Kate", "Kate"),
  year = c(1976, 1995, 1997),
  title = c("1976 \n (Kate Jackson in Charlie's Angels) \n", "1995  \n (Kate Winslet in Sense and Sensibility) \n", "1997 \n (Kate Winslet in Titanic) \n")
)


babynames %>%
  filter(name %in% c( "Kate"), sex == "F") %>%
  filter(year>=1950) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = title),
             linetype = "dashed",
             data = winslet,
             size = 1) + 
   labs(title = "Girls Named Kate: Charlie's Angels and Other Influences", subtitle = "Kate Jackson and Kate Winslet", y = "babies")
ggsave("katejackson.png")


jackieo <- data.frame(
  #name = c("Jacqueline", "Jacqueline", "Jaclyn"),
  year = c(1960, 1976),
  title = c("1960 \n Jackie Kennedy \n becomes First Lady \n", "1976 \n Jaclyn Smith  \n stars in Charlie's Angels \n" )
  
)

babynames %>%
  filter(name %in% c( "Jaclyn", "Jacqueline")) %>%
  filter(year>=1950, sex == "F") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = title),
             linetype = "dashed",
             data = jackieo,
             size = 1) + 
  labs(title = "Girls Named Jaclyn or Jacqueline: Charlie's Angels and Other Influences", subtitle = "Jaclyn Smith and Jackie Kennedy", y = "babies")
ggsave("jaclynsmith.png")




```
# Full Names and Nicknames

```{r}
babynames %>%
  filter(name %in% c( "Jackie")) %>%
  filter(year>=1950, sex == "F") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = title),
             linetype = "dashed",
             data = jackieo,
             size = 1) + 
  labs(title = "Nickname: Jackie", subtitle = "Influence Jaclyn Smith and Jackie Kennedy", y = "babies")
ggsave("jackie.png")


babynames %>%
  filter(name %in% c( "Catherine"), sex == "F") %>%
  filter(year>=1950) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = title),
             linetype = "dashed",
             data = winslet,
             size = 1) + 
   labs(title = "Full Name: Catherine", subtitle = "Influence of Kate Jackson and Kate Winslet", y = "babies")
ggsave("catherine.png")


babynames %>%
  filter(name %in% c( "Katherine"), sex == "F") %>%
  filter(year>=1950) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = title),
             linetype = "dashed",
             data = winslet,
             size = 1) + 
   labs(title = "Full Name: Katherine", subtitle = "Influence of Kate Jackson and Kate Winslet", y = "babies")
ggsave("Katherine.png")

  
```


# # Reese Witherspoon

# Actress

```{r}
reese <- data.frame(
  year = c(1999, 2001, 2005),
  movie = c("1999 \n Cruel Intentions \n", "2001 \n Legally Blonde \n", "2005 \n Walk The Line \n ")
  
)


babynames %>%
  filter(name %in% c("Reese")) %>%
  filter(year>=1990) %>%
  ggplot() +
   
  #facet_wrap(~sex, scales = "free_y") + 
    geom_vline(aes(xintercept = year, color = movie),
             linetype = "dashed",
             size = 1,
             data = reese) + 
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
     labs(title = "Babies Named Reese: Reese Witherspoon's Influence", y = "babies")

ggsave("namereese.png")

```

#Characters

```{r}

reese_chars <- data.frame(
  name = c("Elle", "June"),
  year = c(2001, 2005),
  movie = c("2001 \n Elle In Legally Blonde \n", "2005 \n June in Walk The Line \n ")
  
)
babynames %>%
  filter(name %in% c("Elle", "June" ), sex == "F") %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = year, color = movie),
             linetype = "dashed",
             size = 1,
             data = reese_chars) + 
     labs(title = "Girls Named Elle and June: Reese Witherspoon's Influence", subtitle = "Characters Reese Witherspoon played in her films ", y = "babies")

ggsave("reesechars.png")


babynames %>% 
  filter(name == "Annette", year>1985)
#Not enough movement for causality with Annette
   
```

# Costars

```{r}
joaquin <- data.frame(
  name = c("Joaquin", "Joaquin", "Johnny"),
  
  year = c(2000, 2005, 2005),
  movie = c("2000 \n Gladiator \n", "2005 \n Walk The Line \n", "2005 \n Walk The Line \n")
  
  
)

  
babynames %>%
  filter(name %in% c("Joaquin", "Johnny"), sex == "M") %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = year, color = movie),
             linetype = "dashed",
             size = 1,
             data = joaquin
             
          )

babynames %>%
  filter(name %in% c("Sebastian", "Ryan")) %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1999),
             linetype = "dashed",
             size = 1
          )

babynames %>%
  filter(name %in% c("Matthew", "Warner", "Emmett", "Luke")) %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 2001),
             linetype = "dashed",
             size = 1
          )
```

# # Casablanca

#Women 
```{r}

babynames %>%
  filter(name %in% c("Ilsa", "Ingrid", "Rick", "Humphrey")) %>%
  filter(year>=1920) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1942),
             linetype = "dashed",
             color = "navy",
             size = 1) + 
       labs(title = "Characters and Actors from Casablanca", subtitle = "Casablanca was released in 1942 ", y = "babies")

  
ggsave("casablanca.png")
  

```
# Men

```{r}

babynames %>%
  filter(name %in% c("Rick", "Richard")) %>%
  
  filter(sex == "M") %>% 
  filter(year>=1920, year <=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = name)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1942),
             linetype = "dashed",
             color = "navy")
  

babynames %>% 
  filter(name == "Richard", year > 1935, sex == "M")
```

```{r}

babynames %>%
  filter(name %in% c("Humphrey")) %>%
  
  filter(sex == "M") %>% 
  filter(year>=1920, year <=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = name)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1942),
             linetype = "dashed",
             color = "navy")
```



# # Buffy

```{r}

#According to https://ohbabynames.com/all-baby-names/xander/, "Xander did not appear on the U.S. popularity charts as an independently given name until 1999"
babynames %>%
  filter(name %in% c("Buffy", "Willow", "Xander", "Angel")) %>%
  filter(year>=1960) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1997),
             linetype = "dashed",
             color = "red", 
             size = 1) +
  geom_vline(aes(xintercept = 2003),
             linetype = "dashed",
             color = "navy", 
             size = 1) + 
  labs(title = "Characters from Buffy the Vampire Slayer", subtitle = "The show began airing in 1997 and ended 2003", y = "babies")
# babynames %>% 
#   filter(name=="Buffy")

ggsave("buffy.png")

  
```






# # Kramer vs Kramer

# Dustin

```{r}
hoffman_movies <- data.frame(
  
  title = c("1967 \n (The Graduate Released) \n", "1969  \n (Midnight Cowboy Released) \n", "1974 \n (Lenny Released) \n", "1976 \n (All The Presidents Men Released) \n", "1979 \n (Kramer vs. Kramer Released) \n"),
  year = c(1967, 1969, 1974, 1976, 1979)
)

babynames %>%
  filter(name %in% c("Dustin")) %>%
  filter(year>=1949, sex == "M") %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  geom_vline(aes(xintercept = year, color = title), linetype = "dashed", data = hoffman_movies, size = 1) + 
    labs(title = "Boys Named Dustin: Influence of Dustin Hoffman", y = "babies")
ggsave("dustin.png")


```


# Meryl

```{r}

babynames %>%
  filter(name %in% c("Meryl")) %>%
  filter(year>=1949) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1979),
             linetype = "dashed",
             color = "red", size = 1) + 
    labs(title = "Girls Named Meryl: Influence of Meryl Streep", subtitle = "Kramer vs. Kramer was released in 1976", y = "babies")

ggsave("meryl.png")


```
```{r}

babynames %>%
  filter(name %in% c("Ted")) %>%
  filter(year>=1949) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1979),
             linetype = "dashed",
             color = "red")

babynames %>%
  filter(name %in% c("Joanna")) %>%
  filter(year>=1949) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1979),
             linetype = "dashed",
             color = "red")

```
# # # On further thought, Unlikely to unclude these in the writeup


# # Disney

#Princesses

```{r}
princess_names <- c("Ariel", "Belle", "Jasmine", "Mulan", "Tiana", "Merida", "Elsa", "Giselle")



princess_yrs <- data.frame(
  name = princess_names, 
  
  year = c(1989, 1991, 1992, 1998, 2009, 2012, 2013, 2007),
  
  release = c("Little Mermaid \n", "Beauty and \n the Beast \n", "Aladdin \n", "Mulan \n", "Princess and \n the Frog \n", "Brave \n", "Frozen \n", "Enchanted \n")
)


babynames %>%
  filter(name %in% princess_names, sex == "F") %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = year, color = release),
             linetype="dashed",
             data = princess_yrs,
             size = 1) + 
  labs(title = "Disney Princesses", subtitle = "Vertical Line Marks Film's Release", y = "babies")

ggsave("disneyprincesses.png")
  
```


# Princes

```{r}
prince_names <- c("Eric", "Adam", "Aladdin", "Shang", "Naveen", "Kristoff", "Flynn") 

prince_yrs <- data.frame(
  name = prince_names, 
  
  year = c(1989, 1991, 1992, 1998, 2009, 2013, 2010),
  
  release = c("Little Mermaid \n", "Beauty and \n the Beast \n", "Aladdin \n", "Mulan \n", "Princess and \n the Frog \n", "Frozen \n", "Tangled \n")
  
  
)

babynames %>%
  filter(name %in% prince_names, sex == "M") %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = year, color = release),
             linetype="dashed",
             size = 1,
             data = prince_yrs) + 
  labs(title = "Disney Princes", subtitle = "Vertical Line Marks Film's Release", y = "babies")

ggsave("disneyprinces.png")
```




# # Gossip Girl

# Characters

```{r}
babynames %>%
  filter(name %in% c("Serena", "Blair", "Blaire", "Dan", "Chuck", "Nate" )) %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
    geom_vline(aes(xintercept = 2007),
             linetype = "dashed",
             color = "red")
```

# Actors

```{r}
babynames %>%
  filter(name %in% c("Blake", "Leighton", "Penn", "Chace", "Chase")) %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 2007),
             linetype = "dashed",
             color = "red")
```
```{r}
babynames %>%
  filter(name %in% c("Serena")) %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~sex, scales = "free_y") + 
  geom_vline(aes(xintercept = 2007),
             linetype = "dashed",
             color = "red") + 
  geom_vline(aes(xintercept = 2011),
             linetype = "dashed",
             color = "red")
  
```

# # Gilmore Girls

```{r}
babynames %>%
  filter(name %in% c("Lorelai", "Rory")) %>%
  filter(year>=1990) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 2000),
             linetype = "dashed",
             color = "navy")
  
  
```
# # Random Tests, Checks, and Numbers

```{r}
babynames %>%
  filter(name %in% c("Phoebe")) %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1994),
             linetype = "dashed",
             color = "navy")

babynames %>%
  filter(name %in% c("Jed")) %>%
  filter(year>=1980) %>%
  ggplot() +
  geom_point(mapping = aes( x=year, y = n, color = sex)) + 
  facet_wrap(~name, scales = "free_y") + 
  geom_vline(aes(xintercept = 1999),
             linetype = "dashed",
             color = "navy")


babynames %>% 
  filter(name == "Luna" | name == "Bellatrix", year >=2000, sex == "F")


babynames %>% 
  filter(name == "Darren", year >=1960) #Darren does move up a little bit for girls as well

         

babynames %>% 
  filter(name == "Tabitha", year >=1960, sex == "F")

babynames %>% 
  filter(name == "Endora", year >=1960, sex == "F")



```




